\chapter{Acknowledgements}

I would like to thank my supervisors Dr. Pilar Tugores, Dr. Miguel Cabenellas-Reboredo, and Dr.
Diego Álvarez-Berastegui for their support and involvement in the development of this study. Their
expertise and guidance were invaluable and I am grateful for the welcoming and encouraging
environment they provided.

\medskip

I would also like to thank ICCAT and Global Fishing Watch for the development of public data
products which greatly enhance the possibilities to understand and monitor human activites at sea.

\medskip

Thanks as well to my friends who helped me find balance during the thesis time, and a special thank
you to Francesca Satolli for her emotional support during the writing process.

\medskip

This research was supported by multiple sources. The main supervisor, Pilar Tugores was funded by a
postdoctoral research grant ``Post-doc Vicenç Mut 2021'' from the ``Govern de les Illes Balears''
(PD/048/2021). Diego Álvarez-Berastegui has been contributing to this work within the framwework of
the project ``DINAMO'': Diseño y evaluación de estrategias dinámicas para mitigar el impacto de las
pesquerías de palangre de superficie sobre el medio pelágico: aplicación de un enfoque
ecosistémico., founded by the Agencia Estatal de Investigacion (PID2021-128169OB-I00). The
``TunaMed Observatory'' initiative \url{https://oostop.wixsite.com/tunamed} within ICCAT
Subcommittee of Ecosystem and Bycatch and the I+D+i TUNAWAVE project, funded by the Ministerio de
Ciencia, Innovación y Universidades, the Agencia Estatal de Investigación and FEDER (Project
PID2022-140403OB-I00 funded by MCIN/AEI/10.13039/501100011033 / FEDER, UE).

\section{Declaration of generative AI and AI assisted technologies}

During the creation of this manuscript the author, Tom Leven, used ChatGPT, an AI language model
developed by OpenAI, to improve coding, and clarity. After using this tool, the author reviewed and
edited the content as needed and takes full responsibility for the content.

